|

### 2021-08-07 prova_knit_finale.Rmd
Knit

    if(ESS<(N/r)){
      epsilon=alpha+beta*x+((tau^2)/4)*((data[t]^2)*exp(-alpha-beta*x)-2)
    weight = w*exp((1/(2*tau^2))*((epsilon)^2-(alpha+beta*x)^2)-((data[t]^2)/2)*exp(-alpha-beta*x)*(1+alpha+beta*x))
    k   = sample(1:N,size=N,replace=TRUE,prob=weight)
    x1   = rnorm(N,alpha+beta*x[k]+(tau^2)/4*((data[t]^2)*exp(-(alpha+beta*x[k]))-2),tau)
    w   = rep(1/N,N)
    }else{
    weight = rep(1/N,N)
    k   = sample(1:N,size=N,replace=FALSE,prob=weight)
    x1   = rnorm(N,alpha+beta*x[k]+(tau^2)/4*((data[t]^2)*exp(-(alpha+beta*x[k]))-2),tau)
    w   <-  w*dnorm(data[t],0,exp(x1))*dnorm(x1,alpha+beta*x[k],tau)/
      dnorm(x1,mean=alpha+beta*x[k]+(tau^2)/4*((data[t]^2)*exp(-(alpha+beta*x[k]))-2),tau)
    }

@@

  }
  return(list(xs=xs,ws=ws,ess=ess))
}
#----------------------------------------------------------------------------------

@@

```{r include=FALSE}
N <- 5000
alpha <- 0
beta  <-  0.99
tau2  =  0.05
tau   = sqrt(tau2)
m0      = 0
C0      = 100
ealpha  = alpha
valpha  = 0.01
ebeta    = beta
vbeta    = 0.01
nu      = 5
lambda  = tau2*3/5

@@

```{r echo=FALSE, fig.align='center', fig.cap="Comparison of filtering strategies for Stochastic Volatility Model. Filtered States with credible interval (in red)", fig.height=6, fig.pos='H', fig.width=8, message=FALSE, warning=FALSE, results=F}
plotone<-SVFiltplot(dfsv,svpf,"",2,-2)
plottwo<-SVFiltplot(dfsv,svgpf,"",2,-2)
plotthree<-SVFiltplot(dfsv,svapf,"",2,-2)
plotfour<-SVFiltplot(dfsv,svlw,"",2,-2)

@@

    if(ESS<(N/r)){
      epsilon=alpha+beta*x+((tau^2)/4)*((data[t]^2)*exp(-alpha-beta*x)-2)
    weight = w*exp((1/(2*tau^2))*((epsilon)^2-(alpha+beta*x))-((data[t]^2)/2)*exp(-alpha-beta*x)*(1+alpha+beta*x))
    k   = sample(1:N,size=N,replace=TRUE,prob=weight)
    x1   = rnorm(N,alpha+beta*x[k]+(tau^2)/4*((data[t]^2)*exp(-(alpha+beta*x[k]))-2),tau)
    w   = rep(1/N,N)
    }else{
    weight = rep(1/N,N)
    k   = sample(1:N,size=N,replace=FALSE,prob=weight)
    x1   = rnorm(N,alpha+beta*x[k]+(tau^2)/4*((data[t]^2)*exp(-(alpha+beta*x[k]))-2),tau)
    w   <-  w*exp((1/(2*tau^2))*((alpha+beta*x[k]+((tau^2)/4)*((data[t]^2)*exp(-alpha-beta*x[k])-2))^2-(alpha+beta*x[k]))-((data[t]^2)/2)*exp(-alpha-beta*x[k])*(1+alpha+beta*x[k]))
    }

>>>>

    if(ESS<(N/r)){
      epsilon=alpha+beta*x+((tau^2)/4)*((data[t]^2)*exp(-alpha-beta*x)-2)
    weight = w*exp((1/(2*tau^2))*((epsilon)^2-(alpha+beta*x)^2)-((data[t]^2)/2)*exp(-alpha-beta*x)*(1+alpha+beta*x))
    k   = sample(1:N,size=N,replace=TRUE,prob=weight)
    x1   = rnorm(N,alpha+beta*x[k]+(tau^2)/4*((data[t]^2)*exp(-(alpha+beta*x[k]))-2),tau)
    w   = rep(1/N,N)
    }else{
    weight = rep(1/N,N)
    k   = sample(1:N,size=N,replace=FALSE,prob=weight)
    x1   = rnorm(N,alpha+beta*x[k]+(tau^2)/4*((data[t]^2)*exp(-(alpha+beta*x[k]))-2),tau)
    w   <-  w*dnorm(data[t],0,exp(x1))*dnorm(x1,alpha+beta*x[k],tau)/dnorm(x1,mean=alpha+beta*x[k]+(tau^2)/4*((data[t]^2)*exp(-(alpha+beta*x[k]))-2),tau)
    }

@@

#----------------------------------------------------------------------------------

@@

```{r include=FALSE}
N <- 10000
alpha <- 0
beta  <-  0.99
tau2  =  0.05
tau   = sqrt(tau2)
m0      = 0
C0      = 100
ealpha  = alpha
valpha  = 0.01
ebeta    = beta
vbeta    = 0.01
nu      = 5
lambda  = tau2*3/5

@@

```{r echo=FALSE, fig.align='center', fig.cap="Comparison of filtering strategies for Stochastic Volatility Model. Filtered States with credible interval (in red)", fig.height=6, fig.pos='H', fig.width=8, message=FALSE, warning=FALSE, results=F}
plotone<-SVFiltplot(dfsv,svpf,"",3,-3)
plottwo<-SVFiltplot(dfsv,svgpf,"",3,-3)
plotthree<-SVFiltplot(dfsv,svapf,"",3,-3)
plotfour<-SVFiltplot(dfsv,svlw,"",3,-3)

@@

    if(ESS<(N/r)){
      epsilon=alpha+beta*x+((tau^2)/4)*((data[t]^2)*exp(-alpha-beta*x)-2)
      weight = w*exp((1/(2*tau^2))*((epsilon)^2-(alpha+beta*x)^2)-((data[t]^2)/2)*exp(-alpha-beta*x)*(1+alpha+beta*x))
      k   = sample(1:N,size=N,replace=TRUE,prob=weight)
      x1   = rnorm(N,alpha+beta*x[k]+(tau^2)/4*((data[t]^2)*exp(-(alpha+beta*x[k]))-2),tau)
      w   = rep(1/N,N)
    }else{
      weight = rep(1/N,N)
      k   = sample(1:N,size=N,replace=FALSE,prob=weight)
      x1   = rnorm(N,alpha+beta*x[k]+(tau^2)/4*((data[t]^2)*exp(-(alpha+beta*x[k]))-2),tau)
      w   <-  w*dnorm(data[t],0,exp(x1/2))*dnorm(x1,alpha+beta*x[k],tau)/
        dnorm(x1,mean=alpha+beta*x[k]+(tau^2)/4*((data[t]^2)*exp(-(alpha+beta*x[k]))-2),tau)
    }
